Efficient pedigree recording for fast population genetics simulation

### 2017-12-30 forwards_paper.tex
Implement suggestion in #39 to put move fig details to appendix

@@

%%%%%%%%%%%%%%
\subsubsection*{Sequential simplification and prior history}

@@

%% \newpage
%% \clearpage
%% \section*{Supplementary Information}
\renewcommand{\thefigure}{A\arabic{figure}}
\setcounter{figure}{0}

@@

\begin{figure}
    \includegraphics[]{sims/speedup_nosel}
    \caption{\label{sfig:speedup_nosel}Relative performance improvement due to pedigree tracking for simulations without
    selection.  Data points are taken from Figure~\ref{sfig:rawspeed_nosel} and show the ratio of run times tracking
neutral variation over the run times tracking the pedigree.}
\end{figure}

\begin{figure}
    \includegraphics[]{sims/memuse_nosel}
    \caption{\label{sfig:ramnosel}Peak RAM use in gigabytes (GB) for simulations without selection.  The plots are from
    the same data as in Figure \ref{sfig:rawspeed_nosel}.}
\end{figure}
\end{document}

>>>>

Our method uses more RAM use than simple forward simulations (see~\ref{ss:memuse_nosel}),
although in practice shorter simplification intervals may reduce RAM use
(but at a slight cost to the speed up achieved, see~\ref{ss:seq_simp}).
The benefits to our method are not limited to situations with selection:
in a more limited set of neutral simulations we found the same qualitative
behavior with a numerically larger benefit to pedigree tracking (see~\ref{ss:speedup_nosel}).

@@

%%%%%%%%%%%%%%
\subsubsection*{Sequential simplification and prior history}
\label{ss:seq_simp}

@@

%% \newpage
%% \clearpage
%% \section*{Supplementary Information}

\section{Memory usage with selection}
\label{ss:memuse}
\renewcommand{\thefigure}{B\arabic{figure}}
\setcounter{figure}{0}

\begin{figure}
    \includegraphics[]{sims/memuse_nosel}
    \caption{\label{sfig:ramnosel}Peak RAM use in gigabytes (GB) for simulations without selection.  The plots are from
    the same data as in Figure \ref{sfig:rawspeed_nosel}.}
\end{figure}

\section{Timing with no selection}
\label{ss:timing_nosel}
\renewcommand{\thefigure}{C\arabic{figure}}
\setcounter{figure}{0}

@@

\begin{figure}
    \includegraphics[]{sims/speedup_nosel}
    \caption{\label{sfig:speedup_nosel}Relative performance improvement due to pedigree tracking for simulations without
    selection.  Data points are taken from Figure~\ref{sfig:rawspeed_nosel} and show the ratio of run times tracking
neutral variation over the run times tracking the pedigree.}
\end{figure}
\end{document}
